### 2020-11-17 paper/draft1.tex
wrote out definitions

\section{Definitions}
We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_i \in \{0, 1\}$ for $1 \leq i \leq m$. Specifically, let $\theta_i = P(X_i = 1) = 1 - P(X_i = 0)$. For each event event, we draw the outcome for the event $x_i \sim X_i$. We say event $i$ occurred when and only when $x_i = 1$.

define selection mechanism

define accuracy

@@

define truthful mechanism
A scoring mechanism is truthful iff, for all forecasters, their respective probability of being selected as the best overall forecaster is maximized when their reports match their beliefs for all events.

define accuracy gap

define $m_\delta$

>>>>

\section{Definitions}
We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_k \in \{0, 1\}$ for $1 \leq k \leq m$. Specifically, let $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$. For each event, we draw the outcome for the event $x_k \sim X_k$. We say event $k$ occurs when and only when $x_i = 1$. There are $n$ participants in the forecasting competition. Each forecaster independently submits a vector of predictions $y_i \in [0, 1]^m$, such that $y_{i, k}$ is forecaster $i$'s estimate of $\theta_k$. We call these $y_i$ the forecasts of the $i$th forecaster.

A forecasting mechanism $M(y, x)$ maps the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_k)$ to an index $w \in [1, n]$. We say that forecaster $w$ wins the competition if $M(y, x) = w$. Next, we consider some properties that an ideal mechanism would have.

We call a mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts. Specifically, let $\hat{\theta}_{i, k}$ be forecaster $i$'s belief of the value $\theta_k$. We say that $M$ is truthful if for any $y_i \neq \hat \theta_{i}$,
\[ P(M( (y_1, ..., \hat \theta_i, .., y_n), x ) = i) \geq  P(M( (y_1, ..., \hat y_i, .., y_n), x ) = i)\]
and we say $M$ is strictly truthful if the strict inequality holds.

Additionally, we would like our mechanism to choose the forecaster with the best predictions. We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities. Specifically, $a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$. An ideal mechanism would choose forecasters with larger accuracies with higher probabilities. Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$. We call $\epsilon = a^* - \max_{i \neq i^*} a_i$ the accuracy gap. $\epsilon$ is the difference in accuracy between the best and second best forecaster.

For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$. Specifically, for any $m > m_\delta(M, n, \epsilon)$, $P(M(y, x) \neq i^*) \leq \delta$. $m_\delta$ gives us a measure of how many events are needed for a mechanism to stably pick the best forecaster. We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.

@@
